Elicitation Complexity via Convex Piecewise Linear Loss Functions

### 2018-10-29 jessie-writeup/jessie-writeup.tex
Small tweaks and trimming down my writeup... pun intended

%	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
%	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
%	Observe that $\R'$ is finite and nonempty.
	Construct the finite set $\R' = \{\Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{TODO- Check this is how we want to construct $\R'$.}
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.
%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
%	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.

	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set (b.) a proper subset of another level set, or (c.) span multiple level sets.
	Removing redundant reports resolves (a.) and (b.).
	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
	\jessie{... to do}

	Therefore, there will be at least one $r \in \R'$ per distribution, and as level sets are closed, so $\gamma$ will still be nondegenerate.
	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.

@@

\begin{proof}
	Let $\gamma: \P \toto \R'$, and $\Gamma: \P \toto \reals^d$.
	For contradiction, suppose there was some other nondegenerate, nonredundant $\zeta: \P \toto \R$ so that $\zeta \preceq \Gamma$.
	For any $\zeta \approx \gamma$, we know $\strip(\zeta) = \strip(\gamma)$.
	If $\zeta \not \approx \gamma$, then $\card(\R') \neq \card(\R)$.
	If $\card(\R') > \card(\R)$, then we either contradict nondegeneracy of $\zeta$ or nonredundancy of $\gamma$ and contradict nondegeneracy of $\gamma$ or nonredundancy of $\zeta$ with the other direction of inequality.
	Thus, we must have $\gamma \approx \zeta$, and conclude $\strip(\gamma)$ is unique.

@@

	\jessie{Begin J-embedding}
	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
	Therefore, it is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\zeta)$.
	We know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
	Therefore, for every $r \in \reals^d$, there is some $r' \in \reals^d$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'} \iff p \in \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$ as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
	\jessie{End J-embedding}
\end{proof}

@@

\jessie{Begin J-embedding}
By Conjecture~\ref{conj:gam-prime-exists}, there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
\jessie{End J-embedding}

@@

\item [$1 \implies 6$]
Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of J-embedding and $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\begin{definition}\label{def:unlabeled-nonredundant}
	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
	%  \raft{Have not defined elicitability for unlabeled properties.  Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?  I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.  JF: you're right... shoot}
	\jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma~\ref{lem:nonredundant-defs-equivalent}.}
\end{definition}

\begin{lemma}\label{lem:nonredundant-defs-equivalent}
	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
\end{lemma}
\begin{proof}
	If the property $\Gamma$ is nonredundant, there is a bijection $\varphi:\R \toto \P$ so that $\varphi(r) = \Gamma_r$ and $\varphi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \varphi(r_i), \theta_j = \varphi(r_j)$ so that $\theta_i \subseteq \theta_j$.

	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \varphi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ 	
	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}

%	We show both directions.\\
%	\begin{enumerate}
%		\item [$\implies$]
%		Let the property $\Gamma:\P \to \R$ be nonredundant.
%		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
%
%		For each $r_i \in \R$ we know that there is a level set $\theta_i$ corresponding to the labeled level set $\Gamma_{r_i}$.
%		As there is no level set $\theta$ that does not correspond to some $r \in \R$ by nondegeneracy of $\Gamma$ and no $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ for $i \neq j$, then there are no corresponding level sets so that $\theta_i \subseteq \theta_j$.
%		
%		
%		\item[$\impliedby$] 
%		Say that for there are no distinct full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\theta \subseteq \theta'$.
%		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
%		
%		\jessie{Come back later if needed}
%
%		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
%	\end{enumerate}

\begin{lemma}\label{lem:pos-measure-iff-nonempty-int}
Let $S$ be a convex set.
$S$ has nonempty interior $\implies$ has positive Lebesgue measure.
\end{lemma}
\begin{proof}

%%%\begin{enumerate}
%%%	\item[$\implies$]
	Let $S$ have nonempty interior.
	We know that as $\inter{S}$ and $bd(S)$ are disjoint, $\mu(S) = \mu(\inter{S}) + \mu(bd(S))$.
	Since the interior of $S$ is nonempty, there is an open ball $B \subseteq S$ such that $x \in B \implies x \in \inter S$.
	As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
	As $0 < \mu(B) \leq \mu(\inter S) \leq \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.

%%%	\item[$\impliedby$]  		
%%%	Follows from the contrapositive and definition of measure.
%%%%		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
%%%%		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.

%%%		\jessie{Use Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.}
%%%	\end{enumerate}
\end{proof}

>>>>

%	To start, construct $\R' := \{ r \in \R : \inter{\Gamma_r} \neq \emptyset \} \subseteq \R$.
%	Since $\card(\R') \leq \card(\reals^d)$, there is an injection $\varphi:\R' \to \reals^d$.
%	Observe that $\R'$ is finite and nonempty.
	Construct the finite set $\R' = \{\Gamma(p) : p \in \inter{\theta} \}_{\theta \in \Theta}$. \jessie{TODO- Check this is how we want to construct $\R'$.}
	(If $\R'$ is not finite, choose just one $r \in \R$ so that $\theta = \Gamma_r$.)
	Defining the property $\gamma : p \mapsto \Gamma(p) \cap \R'$, we see that $\gamma \preceq \Gamma$.
	We want to show that the constructed $\gamma$ is nondegenerate and nonredundant.
	As $\Gamma$ is nondegenerate, there is some report $r \in \reals^d$ such that $r \in \Gamma(p)$.
	For every $p \in \P$, there is some level set $\theta$ so that $p \in \cl{\theta}$, and since level sets of elicitable properties are closed (see Lemma~\ref{lem:closed-level-sets}), and therefore $p \in \theta$.
	Thus there is some report $r \in \R'$ so that $r \in \gamma(p)$, so $\gamma$ is nondegenerate.
%	If $p \in \inter{\Gamma}_r$, then by construction of $\R'$, we see $r \in \R'$.
%	Since level sets are closed, for any $r \in \R'$, we know that $\varphi(r) \in \Gamma(q)$ for all $q \in bd(\Gamma_{\varphi(r)})$, and therefore there is at least one report $r \in \R'$ such that $\varphi(r) \in \Gamma(p)$ for all $p \in \P$, so $\gamma$ is nondegenerate.

	If $\gamma$ is redundant, then remove any redundant reports from $\R'$.
	Any level set with a redundant report must either (a.) equal to another level set or (b.) a proper subset of another level set. %, or (c.) span multiple level sets. %not by current definition of redundancy
	Removing redundant reports resolves (a.) and (b.).
%	As $\Gamma$ is elicitable, we can see that (c.) cannot happen.
%	First consider that any redundant report $r$ spanning multiple level sets cannot be full dimensional, as we would contradict elicitability of $\Gamma$ as the score $G$ must be convex, and therefore differentiable almost everywhere in the simplex.
%	If the level set $\Gamma_r \subseteq \Gamma_{r_1}$ or $\Gamma_{r_2}$ for $r_1$ and $r_2 \in \R'$, then we have case (b.).
%	If there is some $p \in \Gamma_r$ so that $p \not \in \Gamma_{r_1} \cap \Gamma_{r_2}$, but there is some $p \in \Gamma_{r_1} \cap \Gamma_r$ and $q \in \Gamma_{r_2} \cap \Gamma_r$, then there must be some $s \in \Gamma_r \cap \Gamma_{r_1} \cap \Gamma_{r_2}$ as the level set $\Gamma_r$ must be convex.
%	At $s$, the	subgradient set of the score $G$ is a two-dimensional closed and convex set, 
%	\jessie{... to do}

	Therefore, there will be at least one $r \in \R'$ per distribution, and since level sets are closed, $\gamma$ will still be nondegenerate.
	Therefore, our constructed $\gamma$ is nondegenerate, nonredundant, and $\gamma \preceq \Gamma$.

@@

\begin{proof}
	Let $\gamma: \P \toto \R'$, and $\Gamma: \P \toto \reals^d$.
	For contradiction, suppose there was some other nondegenerate, nonredundant $\zeta: \P \toto \R$ so that $\zeta \preceq \Gamma$.
	For any $\zeta \approx \gamma$, we know $\strip(\zeta) = \strip(\gamma)$.
	If $\zeta \not \approx \gamma$, there is no bijection from $\R$ to $\R'$, so then $\card(\R') \neq \card(\R)$.
	If $\card(\R') > \card(\R)$, then we either contradict nondegeneracy of $\zeta$ or nonredundancy of $\gamma$ and contradict nondegeneracy of $\gamma$ or nonredundancy of $\zeta$ with the other direction of inequality.
	Thus, we must have $\gamma \approx \zeta$, and conclude $\strip(\gamma)$ is unique.

@@

	\jessie{Begin J-embedding}
	Since $\Gamma$ embeds $\gamma$, there is a nondegenerate, nonredundant $\zeta: \P \toto \R$ for $\R \subseteq \reals^d$ so that $\zeta \preceq \Gamma$ and $\zeta \approx \gamma$.
	Therefore, it is sufficient to show $\theta \in \strip(\Gamma) \implies \theta \in \strip(\zeta)$.
	%Since $\zeta \preceq \Gamma$, we know for all $p \in \P$ that $\zeta(p) \subseteq \Gamma(p)$.
	Therefore, for every $r \in \reals^d$, there is some $r' \in \R$ so that $ p \in \theta = \Gamma_r = \{ p \in \P : r \in \Gamma(p) \} \subseteq \Gamma_{r'} \implies p \in \Gamma_{r'}$ since if $r \not \in \R$ it is a redundant report, so its level set is a subset or equal to another level set for a report in $\R$.
	For $r' \in \R$, we know $p \in \Gamma_{r'} \implies p \in \{ p \in \P : r' \in \Gamma(p) \cap \R \} = \{ p \in \P : r' \in \zeta(p) \} = \zeta_{r'}$. %as $\zeta(p) \subseteq \Gamma(p)$ by closure of level sets (since if a level set is lower-dimensional, there is some full-dimensional level set that it is a subset of).
	\jessie{End J-embedding}
\end{proof}

@@

\jessie{Begin J-embedding}
Since $\Gamma$ has a finite set of full-dimensional level sets comprising $\trim(\Gamma)$ that union to $\P$ (by nondegeneracy of $\Gamma$), we can apply Conjecture~\ref{conj:gam-prime-exists} to notice there is a nondegenerate, nonredundant $\gamma \preceq \Gamma$, and we trivially know that $\gamma \approx \gamma$, so we conclude the property $\gamma$ constructed in Conjecture~\ref{conj:gam-prime-exists} is embedded by $\Gamma$.
\jessie{End J-embedding}

@@

\item [$1 \implies 6$]
Since there is a nondegenerate, nonredundant property $\zeta \preceq \Gamma$ and $\strip(\zeta) = \trim(\Gamma)$ by the definition of J-embedding and assumption that $\zeta$ is finite, we know $\trim(\Gamma)$ is finite.
Additionally, we know that $L|_{\R'}$ elicits $\trim(\Gamma)$ from \emph{cvx-fin-notes.tex}.

@@

\begin{definition}\label{def:unlabeled-nonredundant}
	An unlabeled property $\Theta$ is \emph{nonredundant} if for there are no full dimensional level sets $\theta_1, \theta_2 \in \Theta$ so that $\theta_1 \subseteq \theta_2$.
	%  \raft{Have not defined elicitability for unlabeled properties.  Also, what does ``almost everywhere'' mean in this context, since $\Theta$ is just a set of sets?  I think we just want to say that there are no distinct $\theta_1,\theta_2 \in \Theta$ such that $\theta_1 \subseteq \theta_2$.  JF: you're right... shoot}
	\jessie{Equivalent to definition of nonredundancy for labeled property $\Gamma$, shown in Lemma commented out below.}
\end{definition}

%\begin{lemma}\label{lem:nonredundant-defs-equivalent}
%	An elicitable property $\Gamma$ with finite level sets is nonredundant (in the labeled definition) $\iff$ $\strip(\Gamma)$ is nonredundant (in the unlabeled definition.)
%\end{lemma}
%\begin{proof}
%	If the property $\Gamma$ is nonredundant, there is a bijection $\varphi:\R \toto \P$ so that $\varphi(r) = \Gamma_r$ and $\varphi^{-1}(\theta_i) = r_i$ for each level set $\theta_i \in \Theta = \strip(\Gamma)$.
%	Therefore, if there are no $r_i, r_j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ then there are no level sets $\theta_i = \varphi(r_i), \theta_j = \varphi(r_j)$ so that $\theta_i \subseteq \theta_j$.
%	
%	Similarly, if there is no $\theta_i \subseteq \theta_j$, then there are labels for each $i$ so that $r_i = \varphi^{-1}(\theta_i)$ and there is no distinct $i,j$ so that $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ 	
%	\jessie{This proof doesn't really need to be in here, but it's already typed up, so...}
%	
%%	We show both directions.\\
%%	\begin{enumerate}
%%		\item [$\implies$]
%%		Let the property $\Gamma:\P \to \R$ be nonredundant.
%%		Then for any two reports $r, r' \in \R$ with $r \neq r'$, the level sets $\theta := \Gamma_r \not \subseteq \Gamma_{r'}$ and $\theta' := \Gamma_{r'} \not \subseteq \Gamma_r$.
%%
%%		For each $r_i \in \R$ we know that there is a level set $\theta_i$ corresponding to the labeled level set $\Gamma_{r_i}$.
%%		As there is no level set $\theta$ that does not correspond to some $r \in \R$ by nondegeneracy of $\Gamma$ and no $\Gamma_{r_i} \subseteq \Gamma_{r_j}$ for $i \neq j$, then there are no corresponding level sets so that $\theta_i \subseteq \theta_j$.
%%		
%%		
%%		\item[$\impliedby$] 
%%		Say that for there are no distinct full dimensional level sets $\theta, \theta' \in \Theta := \strip(\Gamma)$ that $\theta \subseteq \theta'$.
%%		Then there are reports $r, r' \in \R$ such that $\theta = \Gamma_r$ and $\theta' = \Gamma_{r'}$.
%%		
%%		\jessie{Come back later if needed}
%%
%%		Therefore, $\strip(\Gamma)$ is nonredundant $\implies \Gamma$ is nonredundant.
%%	\end{enumerate}
%	
%\end{proof}

%\begin{lemma}\label{lem:pos-measure-iff-nonempty-int}
%Let $S$ be a convex set.
%$S$ has nonempty interior $\implies$ has positive Lebesgue measure.
%\end{lemma}
%\begin{proof}
%
%%%%\begin{enumerate}
%%%%	\item[$\implies$]
%	Let $S$ have nonempty interior.
%	We know that as $\inter{S}$ and $bd(S)$ are disjoint, $\mu(S) = \mu(\inter{S}) + \mu(bd(S))$.
%	Since the interior of $S$ is nonempty, there is an open ball $B \subseteq S$ such that $x \in B \implies x \in \inter S$.
%	As Lebesgue measure in $\reals^n$ is a product measure and every open interval has positive measure, then the Lebesgue measure of the ball $B$ is the product of finitely many positive measures, and therefore positive.
%	As $0 < \mu(B) \leq \mu(\inter S) \leq \mu(S)$ by monotonicity, we see that $S$ with nonempty interior has positive measure.
%	
%%%%	\item[$\impliedby$]  		
%%%%	Follows from the contrapositive and definition of measure.
%%%%%		That is, $\mu(S) = \mu(\inter{S}) + \mu(bd(S)) = \mu(\inter{S})$.\footnote{Since $S$ is convex, $\mu(bd(S)) = 0$ according to \url{https://math.stackexchange.com/questions/613408/when-does-the-boundary-have-measure-zero}.}
%%%%%		As $\inter{S} = \emptyset \implies \mu(\inter{S}) = 0$, and hence does not have positive measure.
%	
%%%%		\jessie{Use Lemma~\ref{lem:nonempty-inter-iff-aff-ind}.}
%%%%	\end{enumerate}
%\end{proof}
